\begin{abstract}
Powered wheelchairs are becoming increasingly commonplace in the modern world. However, a major issue faced by powered wheelchair users (PWUs) is navigating the device in crowded areas. Controlling the powered wheelchair in crowded areas requires increased concentration from the PWU, as people in crowds often move unpredictably, or are hidden from view due to standing behind another person or object.

\paragraph{}This project utilizes computer vision techniques to predict the direction of travel of individuals in crowds, and implements an augmented reality system using the Microsoft Hololens that aids the PWU by displaying visual aids that indicate the motion of people. The system further aids the user by warning the user of potential collisions, allowing the PWU to make better navigation decisions. The project also explores the use of the system as a method of assistive control of the wheelchair, preventing collisions by stopping the powered wheelchair should the PWU not notice an individual crossing their path.

\paragraph{}The result of this project is an augmented reality system prototype that can be used to aid navigation for PWU. Our testing shows that the implemented system is able to detect collision risks in a controlled environment and react appropriately using only a visual camera input. Through our experiences, we discuss the disadvantages of relying on only one form of sensor input for obstacle avoidance and the limitations of using the current generation of augmented reality headset as navigational aids.
\end{abstract}
