\newpage

\paragraph{Acknowledgements} This is for a few people

\paragraph{}To Professor Yiannis Demiris, thank you for giving me the freedom to shape this project as I liked. You allowed me to explore fields that interest me and gave me the opportunity to work with the Hololens and other devices that would normally be out of reach. This project has re-ignited my passion for engineering, problem solving and making things work.

\paragraph{}To Rodrigo, Mark and Yong, thank you for always being willing to answer my questions, guiding me through the maze that is Unity, Hololens and ROS development. Without your help and support, this project would not have been possible.

\paragraph{}To my friends and colleagues on the 5\textsuperscript{th} floor office, Marek, Shrey, Tom, Zihan, Ian \& Abdullah, thank you for sitting there with me as we worked on our seperate final year projects. We have laughed, we have stressed but ultimately we have all become friends. I will miss coming into the office everyday and talking with you guys, and I wish you all the best of luck in whatever you choose to pursue.

\paragraph{}To my Mum and Dad, Dian and Bawa, thank you for all the sacrifices you have made to give me the oppurtunity to study at this prestigious university. I have never admitted it, but Dad, I have always seen you as a rolemodel to beat, and I have tried and will continue to try to surpass the expectations you have set. I will never be able to repay you for everything you have done for me, but I will continue to strive to make you both proud.

\paragraph{}To my younger brother Ammar, who is about to start university, thank you for being my brother. You have always supported me and despite our quarrels and disagreements, I could not ask for a better sibling. I hope you do well in university, and that you enjoy your time there.

